---
title: "A/B Testing"
author: "Chloe Shin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.align = "center")
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 68), tidy = TRUE)
knitr::opts_chunk$set(message = FALSE)
set.seed(0)
```

## Data Preparation
```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(knitr)
library(scales)
library(lubridate)
```
```{r}
control <- read.csv("/Users/chloeshin/Downloads/archive/control_group.csv", sep = ";")
test <- read.csv("/Users/chloeshin/Downloads/archive/test_group.csv", sep = ";")
```

```{r}
colnames(control) <- c("Campaign", "Date", "Spend", "Impressions", "Reaches", "Clicks", "Searches", "Views", "Cart", "Purchases")
colnames(test) <- colnames(control)

df <- rbind(control, test)
df$Date <- dmy(df$Date)

df <- df %>%
  distinct() %>%
  drop_na()
```

## Key Metrics
```{r}
camp_avgs <- df %>%
  group_by(Campaign) %>%
  summarise(avg_imp = mean(Impressions), 
            avg_clicks = mean(Clicks),
            avg_purch = mean(Purchases))
```

### 1. Impressions
```{r}
ggplot(df, aes(x = Date, y = Impressions, color = Campaign, group = Campaign)) +
  geom_line(size = 1) +
  geom_hline(data = camp_avgs, aes(yintercept = avg_imp, color = Campaign), linetype = "dotted", linewidth = 0.7) +
  scale_y_continuous(labels = label_number(scale = 1e-3, suffix = "k")) +
  scale_x_date(date_breaks = "5 days", date_labels = "%m.%d") +
  scale_color_manual(values = c("Control Campaign" = "red", "Test Campaign" = "blue")) +
  labs(
    title = "Daily Impressions",
    x = "Date",
    y = "Number of Impressions",
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15)),
    legend.position = "bottom"
)
```

### 2. Clicks
```{r}
ggplot(df, aes(x = Date, y = Clicks, color = Campaign, group = Campaign)) +
  geom_line(size = 1) +
  geom_hline(data = camp_avgs, aes(yintercept = avg_clicks, color = Campaign), linetype = "dotted", linewidth = 0.7) +     
  scale_y_continuous(labels = label_number(scale = 1e-3, suffix = "k")) +
  scale_x_date(date_breaks = "5 days", date_labels = "%m.%d") +
  scale_color_manual(values = c("Control Campaign" = "red", "Test Campaign" = "blue")) +
  labs(
    title = "Daily Clicks",
    x = "Date",
    y = "Number of Clicks",
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15)),
    legend.position = "bottom"
)
```

### 3. Purchases
```{r}
ggplot(df, aes(x = Date, y = Purchases, color = Campaign, group = Campaign)) +
  geom_line(size = 1) +
  geom_hline(data = camp_avgs, aes(yintercept = avg_purch, color = Campaign), linetype = "dotted", linewidth = 0.7) +
  scale_x_date(date_breaks = "5 days", date_labels = "%m.%d") +
  scale_color_manual(values = c("Control Campaign" = "red", "Test Campaign" = "blue")) +
  labs(
    title = "Daily Purchases",
    x = "Date",
    y = "Number of Purchases",
  ) +
  theme_minimal() + 
  theme(
    plot.title = element_text(margin = margin(b = 20), size = 15, face = "bold"),
    axis.title.x = element_text(margin = margin(t = 15)),
    axis.title.y = element_text(margin = margin(r = 15)),
    legend.position = "bottom"
)
```

## Marketing KPIs

```{r}
kpi_sum <- df %>%
  group_by(Campaign) %>%
  summarise(
    avg_CTR = round((sum(Clicks) / sum(Impressions)) * 100, digits = 2),
    avg_CVR = round((sum(Purchases) / sum(Clicks)) * 100, digits = 2),
    avg_CPC = round((sum(Spend) / sum(Clicks)), digits = 2),
    avg_CPP = round((sum(Spend) / sum(Purchases)), digits = 2)
  )

kable(kpi_sum, col.names = c(" ", "Click Through Rate", "Conversion Rate", "Cost Per Click", "Cost Per Purchase"))
```

## Hypothesis Testing

H0: There is no statistically significant difference (KPI) between control and test campaigns.
Ha: There is a statistically significant difference (KPI) between control and test campaigns.

### 1. Click Through Rate  
```{r}
ctr_cvr <- df %>%
  group_by(Campaign) %>%
  summarise(
    tot_imp = sum(Impressions), 
    tot_clicks = sum(Clicks),
    tot_purch = sum(Purchases)
  )
```

```{r}
ctr_test <- prop.test(ctr_cvr$tot_clicks, ctr_cvr$tot_imp)
ctr_test
```
Test Campaign has a significantly higher click through rate compared to control campaign. It is more engaging and relevant to the audience. 

### 2. Conversion Rate
```{r}
cvr_test <- prop.test(ctr_cvr$tot_purch, ctr_cvr$tot_clicks)
cvr_test
```
Test Campaign has a significantly higher conversion rate compared to control campaign. Users are more likely to purchase after landing at the test campaign. 

### 3. Cost Per Click
```{r}
cpc_cpp <- df %>%
  mutate(
    daily_cpc = Spend / Clicks,
    daily_cpp = Spend / Purchases
  )
```

```{r}
cpc_test <- t.test(daily_cpc ~ Campaign, data = cpc_cpp)
cpc_test
```

There is no significant difference in cost per click between two campaigns. 

```{r}
qqnorm(cpc_cpp$daily_cpc)
qqline(cpc_cpp$daily_cpc, col = "red")
```

### 4. Cost Per Purchase
```{r}
cpp_test <- t.test(daily_cpp ~ Campaign, data = cpc_cpp)
cpp_test
```

There is no significant difference in cost per purchase between two campaigns. 

```{r}
qqnorm(cpc_cpp$daily_cpp)
qqline(cpc_cpp$daily_cpp, col = "red")
```

Test campaign is much efficient than the control campaign, as it has significantly higher CTR and CVR while paying the same price for each click and purchases.  

